Fractional Types

### 2019-11-21 fracGC/p.tex
outline of space section done; now polish
thought about trace

%% for Sec. 5
%% \input{latex/PiMemSemCode.tex}
\input{latex/PiFracMemSemCode.tex}

@@

@@

@@

@@

semantics for PiFracDyn:
\PIFMEMstate{}
\PIFMEMstep{}

@@

>>>>

%% for Sec. 5
\input{latex/PiMemSemCode.tex}
\input{latex/PiFracMemSemCode.tex}

@@

%%
\subsection{Abstract Machine without Fractionals}

@@

\PIMEMcardeq{}

\PIMEMstep{}

%%
\subsection{Abstract Machine with Fractionals}

@@

\PIFMEMstep{}

@@

%% semantics for PiFracDyn:
%% \PIFMEMstate{}
%% \PIFMEMstep{}

@@

About trace, it is remarkable: it says, given a function (possibly
using eta/epsilon so input/output sizes not guaranteed to be the same)
\verb|AxC <-> BxC| hence using \verb|AxC| space for the input and
\verb|BxC| space for output, we can 'trace out' the space used for
\verb|C| and derive a function \verb|A <-> B|. This is true \emph{even
  if} \verb|C| is actually used. See the swap example.
